Network Configuration Synthesis with Abstract Topologies

### 2016-11-09 paper/abstraction/paper.tex
make images smaller:

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
     t       &::=& \$x & \textit{template variable} \\
         &\BNFALT& d.d.d.d/[d..d] ~~~~~~~~~~~~~~~~~~~  & \textit{prefix test} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

@@

\begin{figure*}[t!]
  \begin{minipage}[t]{.2\linewidth}
  \hdr{Policy Automata}{}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer1}{}
      \transition{1}{1}{in}{loop above}
    \end{tikzpicture}

    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer2}{}
      \transition{1}{1}{in}{loop above}
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.4\linewidth}
    \hdr{Concrete Topology}{}
    \includegraphics[width=.7\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.4\linewidth}
    \hdr{Abstract Topology}{}
    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
  \end{minipage}%

  \vspace{2em}
  \begin{minipage}[t]{.6\linewidth}
    \hdr{Concrete Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-con}
  \end{minipage}%
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Abstract Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-abs}

@@

@@

\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}
\newcommand{\Router}[1]{\KW{Router} #1:}
\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
\newcommand{\PEER}{\texttt{peer}}
\newcommand{\PREFIX}{\texttt{prefix}}
\newcommand{\IF}{\texttt{if}}
\newcommand{\THEN}{\texttt{then}}
\newcommand{\COMM}{\texttt{comm}}
\newcommand{\MED}{\texttt{MED}}
\newcommand{\Arrow}{\ensuremath{\leftarrow}}

@@

\begin{figure*}[t!]
  \begin{minipage}[t]{.54\linewidth}
    \hdr{Concrete Configuration}{}
    \begin{code}
      \Router{S1, S2}
        Match[100] \PREFIX=GP1, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow *
        Match[100] \PREFIX=GP2, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow *
        ...
        Match[100] \PREFIX=LP1, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow \{AG1, ..., AL1, ...\}
        Match[100] \PREFIX=LP2, \PEER=\{AG1, ..., AL1, ...\}
          \PEER \Arrow \{AG1, ..., AL1, ...\}
        ...
        Match[110] \PREFIX=0.0.0.0/[0..32], \PEER=P1,
          \PEER \Arrow *, \COMM \Arrow (1,0)
        Match[100] \PREFIX=0.0.0.0/[0..32], \PEER=P2,
          \PEER \Arrow *, \COMM \Arrow (0,1)
        ...
      \end{code}
  \end{minipage}
  %
  \begin{minipage}[t]{.4\linewidth}
    \hdr{Template Configuration}{}
    \begin{code}
      \Router{S}
        Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
          \PEER \Arrow *
        Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
          \PEER \Arrow \{AG, AL\}
        Match[110] 0.0.0.0/[0..32], \PEER=P1,
          \PEER \Arrow *, \COMM \Arrow (1,0)
        Match[100] 0.0.0.0/[0..32], \PEER=P2,
          \PEER \Arrow *, \COMM \Arrow (0,1)
        ...
      \end{code}
  \end{minipage}%

  \caption{Spine configurations for concrete and abstract policies.}
  \label{fig:bgp-configs}
\end{figure*}

@@

@@

  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
  \label{fig:concretization}

\end{figure*}%

>>>>

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{template variable} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

@@

\begin{figure*}[t!]
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Policy Automata}{}
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer1}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 1 DFA};
    \end{tikzpicture}
    ~~~~~
    \begin{tikzpicture}[>=stealth',shorten >=1pt,auto,node distance=2cm,minimum size=.5cm]
      \state{0}{$0$}{              }{}
      \state{1}{$1$}{right of=0}{accepting}
      \transition{0}{0}{out}{loop above}
      \transition{0}{1}{Peer2}{}
      \transition{1}{1}{in}{loop above}
      \node at (1,-1){Rank 2 DFA};
    \end{tikzpicture}%
  \end{minipage}
  %
  ~~~~~~
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Concrete Topology}{}
    \includegraphics[width=.7\columnwidth]{figures/topology-con}
  \end{minipage}%
  %
  \begin{minipage}[t]{.3\linewidth}
    \hdr{Abstract Topology}{}
    \includegraphics[width=.57\columnwidth]{figures/topology-abs}
  \end{minipage}%

  \vspace{1em}
  \begin{minipage}[t]{.6\linewidth}
    \hdr{Concrete Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-con}
  \end{minipage}%
  \begin{minipage}[t]{.4\linewidth}
  \hdr{Abstract Product Graph}{}
    \includegraphics[width=.9\columnwidth]{figures/pg-abs}

@@

\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}
\newcommand{\Router}[1]{\KW{Router} #1:}
\newcommand{\Template}[1]{\KW{Template} #1:}
\newcommand{\REGEX}[1]{\texttt{regex}(#1)}
\newcommand{\PEER}{\texttt{peer}}
\newcommand{\PREFIX}{\texttt{prefix}}
\newcommand{\IF}{\texttt{if}}
\newcommand{\THEN}{\texttt{then}}
\newcommand{\COMM}{\texttt{comm}}
\newcommand{\MED}{\texttt{MED}}
\newcommand{\Arrow}{\ensuremath{\leftarrow}}

\begin{figure}[t!]
  \begin{code}
    \Template{S}
      Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
        \PEER \Arrow *
      Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
        \PEER \Arrow \{AG, AL\}
      Match[110] \PREFIX=true \PEER=\{P1\},
        \PEER \Arrow *, \COMM \Arrow (1,0)
      Match[100] \PREFIX=true \PEER=\{P2\},
        \PEER \Arrow *, \COMM \Arrow (0,1)
      ...
  \end{code}

  \vspace{-2em}
  \begin{code}
    \Router{S1, S2}
      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow *
      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow *
      ...
      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow \{AG1, AL1, ...\}
      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow \{AG1, AL1, ...\}
      ...
      Match[110] \PREFIX=true, \PEER=\{P1\},
        \PEER \Arrow *, \COMM \Arrow (1,0)
      Match[100] \PREFIX=true, \PEER=\{P2\},
        \PEER \Arrow *, \COMM \Arrow (0,1)
      ...
    \end{code}

  \vspace{-1em}
  \caption{Spine template and concrete configurations.}
  \label{fig:bgp-configs}
\end{figure}

@@

@@

@@

%=====================================================
%
%
%  **Concretization**
%
%
%=====================================================

@@

  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
  \label{fig:concretization}
\end{figure*}%
